Derogations and emergency policies

### 2023-03-06 analysis/analysis_h1.qmd
Update analysis notebook to use new targets

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(modelsummary)
library(kableExtra)
library(ordinal)
library(brms)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(bayesplot)
library(patchwork)
library(scales)

@@

# Load targets 
withr::with_dir(here::here(), {
  # Final data
  tar_load(daily_panel)
  tar_load(weekly_panel)
  tar_load(year_week_lookup)

  # Models
  tar_load(m_h1)
  tar_load(m_coef_gof)

  # Plotting functions
  invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
})

@@

```{r tbl-h1, cache=TRUE, warning=FALSE}
modelsummary(pull(m_h1, model, name = nice),
             estimate = "{estimate}",
             statistic = "conf.int",
             fmt = 2, coef_map = m_coef_gof$coef_map, 
             gof_map = m_coef_gof$gof_map,
             metrics = c("none"))
```

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
h1_models_plots <- m_h1 %>% 
  mutate(pred_plot = pmap(list(model, nice, family), ~{
    if (..3 == "cumulative") {
      datagrid(model = ..1,
               year_week_num = 1:69,
               derogation_ineffect = 0:1) %>% 
        add_epred_draws(..1) %>% 
        left_join(year_week_lookup, by = "year_week_num") %>% 
        mutate(derogation_ineffect = factor(derogation_ineffect, 
                                            levels = 0:1,
                                            labels = c("No derogation", "Derogation in effect"),
                                            ordered = TRUE)) %>% 
        ggplot(aes(x = year_week_day, y = .epred, color = .category)) +
        stat_lineribbon(aes(fill = .category), alpha = 0.3) +
        scale_color_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_fill_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        scale_y_continuous(labels = label_percent()) +
        labs(x = NULL, y = "Predicted probability", 
             color = "Severity", fill = "Severity",
             title = ..2) +
        facet_wrap(vars(derogation_ineffect)) +
        theme_pandem()
    } else {
      datagrid(model = ..1,
               year_week_num = 1:69,
               derogation_ineffect = 0:1) %>% 
        add_epred_draws(..1) %>% 
        left_join(year_week_lookup, by = "year_week_num") %>% 
        mutate(derogation_ineffect = factor(derogation_ineffect, 
                                            levels = 0:1,
                                            labels = c("No", "Yes"),
                                            ordered = TRUE)) %>% 
        ggplot(aes(x = year_week_day, y = .epred, color = derogation_ineffect)) +
        stat_lineribbon(aes(fill = derogation_ineffect), alpha = 0.3) +
        scale_color_manual(values = c(clrs[1], clrs[8])) +
        scale_fill_manual(values = c(clrs[1], clrs[8])) +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        scale_y_continuous(labels = label_percent()) +
        labs(x = NULL, y = "Predicted probability", 
             color = "Derogation in effect", fill = "Derogation in effect",
             title = ..2) +
        theme_pandem()
    }
  }))

wrap_plots(h1_models_plots$pred_plot)
```

@@

```{r}
# TODO: Figure out how to work with ordered logit marginal effects
```

>>>>

```{r load-libraries, warning=FALSE, message=FALSE}
library(tidyverse)
library(targets)
library(broom)
library(modelsummary)
library(kableExtra)
library(ordinal)
library(brms)
library(marginaleffects)
library(tidybayes)
library(ggdist)
library(bayesplot)
library(patchwork)
library(colorspace)
library(scales)

@@

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Load targets 
# Final data
tar_load(daily_panel)
tar_load(weekly_panel)
tar_load(year_week_lookup)

# Models
tar_load(m_h1)
tar_load(h1_plot_data)
tar_load(models_tbl_h1)

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

@@

```{r tbl-h1, cache=TRUE, warning=FALSE}
notes <- c(
  "Estimates are median posterior log odds from ordered logistic and binary logistic regression models; 95% credible intervals (highest density posterior interval, or HDPI) in brackets.", 
  "Total \\(R^2\\) considers the variance of both population and group effects;", 
  "marginal \\(R^2\\) only takes population effects into account."
)

modelsummary(models_tbl_h1,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_map,
             gof_map = gof_map,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  kable_styling(htmltable_class = "table-sm light-border") %>% 
  footnote(general = notes, footnote_as_chunk = TRUE)
```

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
h1_plots <- h1_plot_data %>% 
  # Predicted probabilities
  mutate(pred_plot = pmap(list(pred_data, nice, family), \(.data, .nice_name, .family) {
    if (.family == "cumulative") {
      .data %>% 
        ggplot(aes(
          x = year_week_day, y = .epred, ymin = .lower, ymax = .upper,
          color = .category, fill = after_scale(color),
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3) +
        scale_color_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        scale_y_continuous(labels = label_percent()) +
        labs(x = NULL, y = "Predicted probability", 
             color = "Severity", fill = "Severity",
             title = .nice_name) +
        facet_wrap(vars(derogation_ineffect)) +
        theme_pandem()
    } else {
      .data %>% 
        ggplot(aes(
          x = year_week_day, y = .epred, ymin = .lower, ymax = .upper,
          color = derogation_ineffect, fill = after_scale(color),
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3) +
        scale_color_manual(values = c(clrs[1], clrs[8])) +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        scale_y_continuous(labels = label_percent()) +
        labs(x = NULL, y = "Predicted probability", 
             color = "Derogation in effect", fill = "Derogation in effect",
             title = .nice_name) +
        theme_pandem()
    }
  })) %>% 
  # Marginal effects / contrasts
  mutate(mfx_plot = pmap(list(mfx_data, nice, family), \(.data, .nice_name, .family) {
    if (.family == "cumulative") {
      .data %>% 
        mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>%
        ggplot(aes(
          x = year_week_day, y = draw, ymin = .lower, ymax = .upper,
          color = group, fill = after_scale(color),
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3) +
        geom_hline(yintercept = 0, linewidth = 0.5, color = "grey50") +
        scale_color_manual(values = darken(clrs[c(2, 4, 6, 7)], 0.5, space = "combined"), guide = "none") +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        labs(x = NULL,
             y = "Percentage point difference\nin probability of outcome level",
             title = .nice_name) +
        facet_wrap(vars(group), ncol = 2) +
        theme_pandem()
    } else {
      .data %>% 
        mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>%
        ggplot(aes(
          x = year_week_day, y = draw, ymin = .lower, ymax = .upper,
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3, fill = clrs[5], color = clrs[5]) +
        geom_hline(yintercept = 0, linewidth = 0.5, color = "grey50") +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        labs(x = NULL,
             y = "Percentage point difference\nin probability of outcome",
             title = .nice_name) +
        theme_pandem()
    }
  }))

wrap_plots(h1_plots$pred_plot)
```

@@

```{r}
wrap_plots(h1_plots$mfx_plot)
```

### 2023-03-06 analysis/analysis_h2.qmd
Update analysis notebook to use new targets

# Load targets
withr::with_dir(here::here(), {
  # Final data
  tar_load(daily_panel)
  tar_load(weekly_panel)
  tar_load(year_week_lookup)

  # Models
  tar_load(m_h2)
  tar_load(m_coef_gof)

  # Plotting functions
  invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
})

@@

```{r tbl-h2, cache=TRUE, warning=FALSE}
modelsummary(pull(m_h2, model, name = nice),
             estimate = "{estimate}",
             statistic = "conf.int",
             fmt = 2, coef_map = m_coef_gof$coef_map, 
             gof_map = m_coef_gof$gof_map,
             metrics = c("none"))
```

@@

### Across time

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
h2_models_plots <- m_h2 %>% 
  mutate(pred_plot = pmap(list(model, nice, family), ~{
    if (..3 == "cumulative") {
      datagrid(model = ..1,
               year_week_num = 1:69,
               derogation_ineffect = 0:1) %>% 
        add_epred_draws(..1) %>% 
        left_join(year_week_lookup, by = "year_week_num") %>% 
        mutate(derogation_ineffect = factor(derogation_ineffect, 
                                            levels = 0:1,
                                            labels = c("No derogation", "Derogation in effect"),
                                            ordered = TRUE)) %>% 
        ggplot(aes(x = year_week_day, y = .epred, color = .category)) +
        stat_lineribbon(aes(fill = .category), alpha = 0.3) +
        scale_color_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_fill_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        scale_y_continuous(labels = label_percent()) +
        labs(x = NULL, y = "Predicted probability", 
             color = "Severity", fill = "Severity",
             title = ..2) +
        facet_wrap(vars(derogation_ineffect)) +
        theme_pandem()
    } else {
      datagrid(model = ..1,
               year_week_num = 1:69,
               derogation_ineffect = 0:1) %>% 
        add_epred_draws(..1) %>% 
        left_join(year_week_lookup, by = "year_week_num") %>% 
        mutate(derogation_ineffect = factor(derogation_ineffect, 
                                            levels = 0:1,
                                            labels = c("No", "Yes"),
                                            ordered = TRUE)) %>% 
        ggplot(aes(x = year_week_day, y = .epred, color = derogation_ineffect)) +
        stat_lineribbon(aes(fill = derogation_ineffect), alpha = 0.3) +
        scale_color_manual(values = c(clrs[1], clrs[8])) +
        scale_fill_manual(values = c(clrs[1], clrs[8])) +
        scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
        scale_y_continuous(labels = label_percent()) +
        labs(x = NULL, y = "Predicted probability", 
             color = "Derogation in effect", fill = "Derogation in effect",
             title = ..2) +
        theme_pandem()
    }
  }))

wrap_plots(h2_models_plots$pred_plot)
```

@@

### Across civil society repression

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
h2_models_plots1 <- m_h2 %>% 
  mutate(pred_plot = pmap(list(model, nice, family), ~{
    if (..3 == "cumulative") {
      datagrid(model = ..1,
               v2csreprss = seq(-2.5, 3, by = 0.1),
               derogation_ineffect = 0:1) %>% 
        add_epred_draws(..1) %>% 
        mutate(derogation_ineffect = factor(derogation_ineffect, 
                                            levels = 0:1,
                                            labels = c("No derogation", "Derogation in effect"),
                                            ordered = TRUE)) %>% 
        ggplot(aes(x = v2csreprss, y = .epred, color = .category)) +
        stat_lineribbon(aes(fill = .category), alpha = 0.3) +
        scale_color_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_fill_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_y_continuous(labels = label_percent()) +
        labs(x = "Civil society repression", y = "Predicted probability", 
             color = "Severity", fill = "Severity",
             title = ..2) +
        facet_wrap(vars(derogation_ineffect)) +
        theme_pandem()
    } else {
      datagrid(model = ..1,
               v2csreprss = seq(-2.5, 3, by = 0.1),
               derogation_ineffect = 0:1) %>% 
        add_epred_draws(..1) %>% 
        mutate(derogation_ineffect = factor(derogation_ineffect, 
                                            levels = 0:1,
                                            labels = c("No", "Yes"),
                                            ordered = TRUE)) %>% 
        ggplot(aes(x = v2csreprss, y = .epred, color = derogation_ineffect)) +
        stat_lineribbon(aes(fill = derogation_ineffect), alpha = 0.3) +
        scale_color_manual(values = c(clrs[1], clrs[8])) +
        scale_fill_manual(values = c(clrs[1], clrs[8])) +
        scale_y_continuous(labels = label_percent()) +
        labs(x = "Civil society repression", y = "Predicted probability", 
             color = "Derogation in effect", fill = "Derogation in effect",
             title = ..2) +
        theme_pandem()
    }
  }))

wrap_plots(h2_models_plots1$pred_plot)
```

@@

```{r}
# TODO: Figure out how to work with ordered logit marginal effects
```

>>>>

# Load targets
# Final data
tar_load(daily_panel)
tar_load(weekly_panel)
tar_load(year_week_lookup)

# Models
tar_load(m_h2)
tar_load(h2_plot_data)
tar_load(models_tbl_h2)

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

@@

```{r tbl-h2, cache=TRUE, warning=FALSE}
notes <- c(
  "Estimates are median posterior log odds from ordered logistic and binary logistic regression models; 95% credible intervals (highest density posterior interval, or HDPI) in brackets.", 
  "Total \\(R^2\\) considers the variance of both population and group effects;", 
  "marginal \\(R^2\\) only takes population effects into account."
)

modelsummary(models_tbl_h2,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_map,
             gof_map = gof_map,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  kable_styling(htmltable_class = "table-sm light-border") %>% 
  footnote(general = notes, footnote_as_chunk = TRUE)
```

@@

@@

```{r fig.width=13, fig.height=6, out.width="100%"}
h2_plots <- h2_plot_data %>% 
  # Predicted probabilities
  mutate(pred_plot = pmap(list(pred_data, nice, family), \(.data, .nice_name, .family) {
    if (.family == "cumulative") {
      .data %>% 
        ggplot(aes(
          x = v2csreprss, y = .epred, ymin = .lower, ymax = .upper,
          color = .category, fill = after_scale(color),
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3) +
        scale_color_manual(values = c(clrs[c(2, 4, 6, 7)])) +
        scale_y_continuous(labels = label_percent()) +
        labs(x = "Civil society repression", y = "Predicted probability", 
             color = "Severity", fill = "Severity",
             title = .nice_name) +
        facet_wrap(vars(derogation_ineffect)) +
        theme_pandem()
    } else {
      .data %>% 
        ggplot(aes(
          x = v2csreprss, y = .epred, ymin = .lower, ymax = .upper,
          color = derogation_ineffect, fill = after_scale(color),
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3) +
        scale_color_manual(values = c(clrs[1], clrs[8])) +
        scale_y_continuous(labels = label_percent()) +
        labs(x = "Civil society repression", y = "Predicted probability", 
             color = "Derogation in effect", fill = "Derogation in effect",
             title = .nice_name) +
        theme_pandem()
    }
  })) %>% 
  # Marginal effects / contrasts
  mutate(mfx_plot = pmap(list(mfx_data, nice, family), \(.data, .nice_name, .family) {
    if (.family == "cumulative") {
      .data %>% 
        mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>%
        ggplot(aes(
          x = v2csreprss, y = draw, ymin = .lower, ymax = .upper,
          color = group, fill = after_scale(color),
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3) +
        geom_hline(yintercept = 0, linewidth = 0.5, color = "grey50") +
        scale_color_manual(values = c(clrs[c(2, 4, 6, 7)]), guide = "none") +
        labs(x = NULL,
             y = "Percentage point difference\nin probability of outcome level",
             title = .nice_name) +
        facet_wrap(vars(group), ncol = 2) +
        theme_pandem()
    } else {
      .data %>% 
        mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>%
        ggplot(aes(
          x = v2csreprss, y = draw, ymin = .lower, ymax = .upper,
          group = forcats::fct_rev(ordered(.width))
        )) +
        geom_lineribbon(alpha = 0.3, fill = clrs[5], color = clrs[5]) +
        geom_hline(yintercept = 0, linewidth = 0.5, color = "grey50") +
        labs(x = NULL,
             y = "Percentage point difference\nin probability of outcome",
             title = .nice_name) +
        theme_pandem()
    }
  }))

wrap_plots(h2_plots$pred_plot)
```

@@

@@

```{r}
wrap_plots(h2_plots$mfx_plot)
```

@@

### 2023-03-06 analysis/analysis_prelim.qmd
Update analysis notebook to use new targets

# Load targets 
withr::with_dir(here::here(), {
  # Final data
  tar_load(daily_panel)
  tar_load(weekly_panel)
  tar_load(year_week_lookup)

  # Models
  tar_load(m_prelim_derog)
  tar_load(m_coef_gof)

  # Plotting functions
  invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
})

@@

```{r tbl-prelim, cache=TRUE}
modelsummary(pull(m_prelim_derog, model, name = nice),
             estimate = "{estimate}",
             statistic = "conf.int",
             fmt = 2, coef_map = m_coef_gof$coef_map, 
             gof_map = m_coef_gof$gof_map,
             metrics = c("R2"))
```

@@

```{r fig.width=12, fig.height=6, out.width="100%"}
preliminary_models_plots <- m_prelim_derog %>% 
  mutate(pred_plot = map2(model, nice, ~{
    datagrid(model = .x,
             year_week_num = 1:69,
             derogation_ineffect = 0:1) %>% 
      add_epred_draws(.x) %>% 
      left_join(year_week_lookup, by = "year_week_num") %>% 
      mutate(derogation_ineffect = factor(derogation_ineffect, 
                                          levels = 0:1,
                                      labels = c("No", "Yes"),
                                      ordered = TRUE)) %>% 
      ggplot(aes(x = year_week_day, y = .epred, color = derogation_ineffect)) +
      stat_lineribbon(aes(fill = derogation_ineffect), alpha = 0.3) +
      scale_color_manual(values = c(clrs[1], clrs[8])) +
      scale_fill_manual(values = c(clrs[1], clrs[8])) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      scale_y_continuous(labels = label_percent()) +
      labs(x = NULL, y = "Predicted probability", 
           color = "Derogation in effect", fill = "Derogation in effect",
           title = .y) +
      theme_pandem()
  }))

wrap_plots(preliminary_models_plots$pred_plot)
```

@@

```{r fig.width=12, fig.height=6, out.width="100%"}
preliminary_models_mfx <- m_prelim_derog %>% 
  mutate(mfx = map(model, ~{
    .x %>% 
      marginaleffects(newdata = datagrid(year_week_num = 1:69),
                      variables = "derogation_ineffect",
                      type = "response") |> 
      posteriordraws()
  })) %>% 
  mutate(mfx_plot = map2(mfx, nice, ~{
    .x %>% 
      left_join(year_week_lookup, by = "year_week_num") %>% 
      ggplot(aes(x = year_week_day, y = draw * 100)) +
      stat_lineribbon(alpha = 0.25, fill = clrs[5], color = clrs[5]) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      labs(x = NULL,
           y = "Percentage point change\nin probability of policy",
           title = .y) +
      theme_pandem()
  }))

wrap_plots(preliminary_models_mfx$mfx_plot)
```

>>>>

tar_config_set(store = here::here('_targets'),
               script = here::here('_targets.R'))

# Load targets 
# Final data
tar_load(daily_panel)
tar_load(weekly_panel)
tar_load(year_week_lookup)

# Models
tar_load(m_prelim_derog)
tar_load(prelim_plot_data)
tar_load(models_tbl_prelim)

# Plotting functions
invisible(list2env(tar_read(graphic_functions), .GlobalEnv))
invisible(list2env(tar_read(modelsummary_functions), .GlobalEnv))

@@

```{r tbl-prelim, cache=TRUE}
notes <- c(
  "Estimates are median posterior log odds from ordered logistic and binary logistic regression models; 95% credible intervals (highest density posterior interval, or HDPI) in brackets.", 
  "Total \\(R^2\\) considers the variance of both population and group effects;", 
  "marginal \\(R^2\\) only takes population effects into account."
)

modelsummary(models_tbl_prelim,
             estimate = "{estimate}",
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_map,
             gof_map = gof_map,
             output = "kableExtra",
             fmt =  list(estimate = 2, conf.low = 2, conf.high = 2)) %>% 
  kable_styling(htmltable_class = "table-sm light-border") %>% 
  footnote(general = notes, footnote_as_chunk = TRUE)
```

@@

```{r fig.width=12, fig.height=6, out.width="100%"}
prelim_plots <- prelim_plot_data %>% 
  mutate(pred_plot = map2(pred_data, nice, ~{
    .x %>% 
      ggplot(aes(x = year_week_day, y = .epred, ymin = .lower, ymax = .upper,
                 color = derogation_ineffect, fill = after_scale(color), 
                 group = forcats::fct_rev(ordered(.width)))) +
      geom_lineribbon(alpha = 0.3) +
      scale_color_manual(values = c(clrs[1], clrs[8])) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      scale_y_continuous(labels = label_percent()) +
      labs(x = NULL, y = "Predicted probability", 
           color = "Derogation in effect", fill = "Derogation in effect",
           title = .y) +
      theme_pandem()
  })) %>% 
  mutate(mfx_plot = map2(mfx_data, nice, ~{
    .x %>% 
      mutate(across(c(draw, .lower, .upper), ~ . * 100)) %>% 
      ggplot(aes(x = year_week_day, y = draw, ymin = .lower, ymax = .upper,
                 group = forcats::fct_rev(ordered(.width)))) +
      geom_lineribbon(alpha = 0.25, fill = clrs[5], color = clrs[5]) +
      scale_x_date(date_breaks = "2 months", date_labels = "%b\n%Y") +
      labs(x = NULL,
           y = "Percentage point difference\nin probability of policy",
           title = .y) +
      theme_pandem()
  }))

wrap_plots(prelim_plots$pred_plot)
```

@@

```{r fig.width=12, fig.height=6, out.width="100%"}
wrap_plots(prelim_plots$mfx_plot)
```
